Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-03-16 index.qmd
update

@@

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/06_corr_julia.ipynb#fig-l-comp >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/06_corr_julia.ipynb#fig-l-j-r-der >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-fit >}}

{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-der >}}
:::

@@

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/05_sea.ipynb#fig-fit >}}

{{< embed notebooks/05_sea.ipynb#fig-fit-params >}}
:::

>>>>

### 03/15/2024

![Discontinuities in log-log scale](figures/l_j_fit_xscale_log)

![Same as above but with multiple time resolutions and time windows](figures/l_j_r_fit_xscale_log)

@@

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/01_results_julia.ipynb#fig-l-comp >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/01_results_julia.ipynb#fig-l-j-r-der >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/01_results_julia.ipynb#fig-l-r-fit >}}
:::

@@

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/archive/05_sea.ipynb#fig-fit >}}

{{< embed notebooks/archive/05_sea.ipynb#fig-fit-params >}}
:::
